Verifying Demonstrations

### 2017-09-21 intro.tex
Edits properties, moves some things to intro

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
The protesters (organizers and participants) have an incentive to increase the 
tallied number of participants, whereas other interests might have an incentive 
to decrease the tallied number of participants, e.g.\ Eve's authoritarian 
regime in our example above.
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks.

@@

Electronic voting (and voting in general) require strong verifiability and 
privacy properties.
We will adapt these requirements to the setting of protests.

>>>>

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
Alice the activist has an incentive to increase the tallied number of 
participants, whereas Eve (and possibly other interests) have an incentive to 
decrease the tallied number of participants.
In this case we have two options:
either we trust Alice or Eve, or we must verify their claims.
We aim for verifiable claims.
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks.

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
These opinions can be sensitive, hence we desire to have similar properties of 
verification and privacy for participation in a protest as there is for voting.

### 2017-09-21 properties.tex
Edits properties, moves some things to intro

\mode*
\section{Desired properties}%
\label{TheIdea}

@@

We have an adversarial setting between Alice the activist and Eve the evil 
regime: Alice wants to show large support against Eve, Eve wants to show little
support for Alice.
In this case we have two options:
either we trust Alice or Eve, or we must verify their claims.
We aim for verifiable claims.

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
These opinions can be sensitive, hence we desire to have similar properties of 
verification and privacy for participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.

>>>>

\mode*
\section{Desired properties}%
\label{Properties}

We categorize the desired properties into verifiability and privacy.

@@

We desire three verifiability requirements:
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each 
  participation proof provides temporal and spatial eligibility and that it has 
  not been counted before.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the submitted participation proofs.
\item\label{IndividualVerif} Individual verifiability: every participant can 
  verify that their participation proof is included in the global count.
\end{requirements}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.
